---
title: "Mini-Project 2"
author: "Carol, Lauren, Neamat"
date: "2019-03-24"
output: 
  html_document:
    code_folding: hide
---

## Data Graphic

```{r, echo=FALSE, message=FALSE}
library(tidyverse)
library(wordcountaddin)
load("house_elections.rda")
load("candidates.rda")
load("committees.rda")
load("contributions.rda")
```

```{r}
# Lauren setting up the Contributions Table for the inner_join()

contributions_clean <- contributions %>%
  filter(transaction_type == "24A" | transaction_type == "24E") %>%
  filter(transaction_amt > 0) %>%
  spread(transaction_type, transaction_amt, fill = 0) %>%
  rename(against = "24A") %>%
  rename(support = "24E") %>%
  select(cand_id, against, support) %>%
  group_by(cand_id) %>%
  summarize(total_for = sum(support), total_against = sum(against))
```

```{r}
# Carol setting up the House Elections Table for the inner_join()

elections <- house_elections %>%
 filter(general_votes > 0, !is.na(fec_id)) %>%
  
 select(fec_id, incumbent, party, general_votes, ge_winner) %>%
  filter(general_votes > 0, !is.na(fec_id)) %>%
  select(fec_id, incumbent, party, general_votes, ge_winner) %>%
  rename(cand_id = fec_id) 

# Neamat added a rename function so joining would be easier
```

```{r}
# Neamat trying to inner_join() by candidate's ids

joined_plot <- inner_join(contributions_clean, elections,
                         by = "cand_id")
```

```{r, warning=FALSE}
# Neamat making it into a rough graph
# Everyone editing this rough graph into a final graph

incumbent_plot <- ggplot(joined_plot, aes(x =(total_for), y = general_votes, color = incumbent)) +
  geom_smooth(method = "lm", se = FALSE, color = "black") +
  geom_jitter() +
  scale_x_log10(name = "Total Contributions per Candidate") +
  scale_y_log10(name = "General Votes per Candidate",
                limits = c(3e+04, 3e+05)) +
  ggtitle("Effectiveness of Campaign Contributions",
          subtitle = "Between Incumbents and Challengers") +
  scale_color_discrete(name = "Incumbent") +
  facet_wrap(~incumbent)

incumbent_plot
```

```{r include=FALSE}
incumbents <- joined_plot %>%
  filter(incumbent == TRUE)

Inc_model <- lm(general_votes~total_for, data = incumbents)
summary(Inc_model)

challengers <- joined_plot %>%
  filter(incumbent == FALSE)

chall_model <- lm(general_votes ~ total_for, data = challengers)
summary(chall_model)
```

These scatter plots shows the correlation between the total funds raised for candidates and the general votes that these candidates received. The plot on the right shows the information for the candidates that are incumbents while the plot on the left shows the information for the candidates that are the challengers. The x and y axis are arranged in logarithmic scales. According to the line of best fit, there is a positive correlation between total contributions for challenger candidates and the general votes raised. There is a negative correlations between the total contributions for incumbent candidates and the general votes raised.

Both correlations are relatively weak and low magnitude, which makes inference difficult and not generally trustworthy. The significance of the negative correlation is so high that there is very little chance of it being pure chance. 
At an alpha level of 0.05, the correlation between the campaign contributions and the general votes of incumbent candidates has such a low p-value that there is definitely a statistically significant negative correlation. We are very confident that the true relationship between campaign contributions and general votes for incumbents is negative, meaning that for every dollar spent in favor of a candidate, the predicted general votes decreases. 
The correlation between the same variables for Challengers is not statistically significant. That does not mean there is no correlation, simply that we cannot prove it does exist. There does not seem to be a significant relationship between contributions and general votes for challengers, implying that the amount spent by challenging candidates is not necessarily related to the amount of votes they got in the general election and that other factors are likely the cause of whether challengers win or lose. 


After further analysis, we’ve found that there was a positive correlation between general votes and the funds raised for a candidate without an incumbent status (as mentioned above), which wasn’t surprising since advertising is usually the major expense for campaigns and they subsequently increase the general votes, though this correlation is not large enough to be significant (source: https://fivethirtyeight.com/features/money-and-elections-a-complicated-love-story/). The fact that funds raised would cause success in an election, however, is not necessarily true since we’ve also found a significant negative correlation between funds and votes for candidates with an incumbent status. But how would spending more money decrease your chances of winning? In the journal article, the **Incumbent Spending Puzzle** (https://www.jstor.org/stable/42864107?seq=3#metadata_info_tab_contents), the author Christopher Magee explains that even though incumbents spend a lot of funds on campaigns, large amounts of funds actually hurts their chances of winning in an election. In fact, he discusses that incumbent funds somewhat depend on their challengers funds; the more money incumbents spend on their campaign, the more they are threatened by their challengers. This means that, since the people have a “perfection perception” of the incumbents from their previous run, the incumbents spending more money only means that they’re being seriously challenged by their opponents. if we had more time to work on this project, we would explore the relationship between incumbents’ funds and votes versus challengers to further analyze that claim. 
> Word count: `r wordcountaddin::word_count()`